Appendix to 'Detecting social information in a dense database of infants’ natural

### 2022-01-06 paper/manuscript/appendix.Rmd

p1 <- ggplot(prf_by_age_faces, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  ylab('F-score') + xlab('Age (months)') +
  ggtitle("Face detections") + 
  theme(legend.position= 'none')

p2 <- ggplot(prf_by_age_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  ylab('F-score') + xlab('Age (months)') +
  ggtitle("Hand detections") + 
  theme(legend.position= 'none')

@@

# density plot of OP's false positive face/hand locations
p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # could actually overplot all the face rectangles? prob very messy...
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Face False Positives") + theme(legend.position = "none") +
  scale_y_reverse()

p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # top-left is 0,0
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Hand False Positives") + theme(legend.position = "none") +
  scale_y_reverse()

>>>>

p1 <- ggplot(prf_by_age_faces, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  theme_few(base_size=12) +
  ylab('F-score') + xlab('Age (months)') +
  ggtitle("Face detections") + 
  theme(legend.position= 'none')

p2 <- ggplot(prf_by_age_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  theme_few(base_size=12) +
  ylab('F-score') + xlab('Age (months)') +
  ggtitle("Hand detections") + 
  theme(legend.position= 'none')

@@

# density plot of OP's false positive face/hand locations
p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # could actually overplot all the face rectangles? prob very messy...
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Face False Positives") + theme(legend.position = "none") +
  scale_y_reverse() +
  theme_few(base_size=12)

p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # top-left is 0,0
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Hand False Positives") + theme(legend.position = "none") +
  scale_y_reverse() +
  theme_few(base_size=12)
